%------------------------
% Resume Template
% Author : Alexander Hahn
% Github : https://github.com/AlexHahnPublic

%------------------------

\documentclass[a4paper,20pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.530in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.45in}
\addtolength{\textheight}{1in}

\urlstyle{rm}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-6pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeItemWithoutTitle}[1]{
  \item\small{
    {\vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{#3} & \textit{#4} \\
    \end{tabular*}\vspace{-5pt}
}


\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-3pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}

\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-----------------------------
%%%%%%  CV STARTS HERE  %%%%%%

\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\LARGE Alexander Hahn}} & Email: \href{mailto:}{afh53@cornell.edu}\\
  \href{https://github.com/AlexHahnPublic}{Github: ~~github.com/AlexHahnPublic} & Mobile:~~~(845) 248-2761 \\
\end{tabular*}

%-----------EDUCATION-----------------
\section{~~Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Cornell University}{Ithaca, New York}
      {Bachelors - Mathematics, concentration in Mathematical Physics}{September 2010 - May 2014}
      %{\scriptsize \textit{ \footnotesize{\newline{}\textbf{Courses:} Operating Systems, Data Structures, Analysis Of Algorithms, Artificial Intelligence, Machine Learning, Networking, Databases}}}
    \resumeSubHeadingListEnd

\vspace{-5pt}
\section{Skills Summary}
        \resumeSubHeadingListStart
        \resumeSubItem{Languages}{~~~~~~R, Haskell, Python, Bash/Unix Commandline tools \& scripting, SQL/kdb, Scala, OCaml}
        \resumeSubItem{Technical}{~~~~~~~~Linux, Git/Travis, Tmux, AWS (S3, EC2, Batch, CloudWatch), MOSEK, Docker, Emacs, Vim, nix, IntelliJ}
        \resumeSubItem{Quantitative}{~~~Statistical Modeling, Quantitative Trading (Execution), Portfolio Construction/Analysis (constrained optimization), Data Processing, Forecasting, Scientific Computing with Linear \& Non-linear Numerical Methods}

\resumeSubHeadingListEnd
\vspace{-5pt}
\section{Experience}
\vspace{2pt}
  \resumeSubHeadingListStart
    \resumeSubheading{Bot Lab LP (Schonfeld external fund)}{New York, NY}
    {Quantitative Trader}{April 2019 - Present}
    \resumeItemListStart

    \resumeItem{Overview} {Built a $\sim$ daily frequency US Equities
      statistical arbitrage strategy alongside a Citadel quant
      portfolio manager (main pm) and Stanford CS PhD (Infra Engineer)
      exclusive to Schonfeld Strategic Advisors. Managed three
      additional employees with a 100MM initial allocation.}

    \resumeItem{Alpha Generation}\\
      $\bullet$ Design and analysis of forecasts across 5 thematic buckets:
      Market Data, Fundamental, Sentiment, Microstructure, and Cross
      Asset.

      $\bullet$ Lead the front to back development of three of our
      eight main signals. Additionally maintained and updated the full
      suite of signals. This entails performance analysis, additional
      feature construction/removal, studies and updates to fitting
      procedures, etc.

      $\bullet$ Built and refined our second layer fit to ensemble the
      base signals into a master signal. Our master signal
      consistently performs well with an In sample correlation with
      the one day forward (residual) return (IC) of 3\%, out of
      sample, 2\%, and in Live 2.5\%.

      $\bullet$ High level areas of current research: Changes to the
      response (forward return residualized to Barra's usfast), new
      alphas/datasets, optimizing prediction frequencies/ multiperiod
      prediction models, applications of statistical learning
      techniques to individual alphas as well as alpha combinations eg
      regularization hyperparameter tuning.

      \resumeItem{Portfolio Construction}\\

      $\bullet$ Helped implement and study our target portfolio
      optimization in MOSEK with studies/prototypes/analysis in R.

      $\bullet$ Objective: choose a target portfolio (TMV
      $\rightarrow$ interger positions) that maximizes expost return
      (single and multiperiod constructions) with a penalty on risk,
      trading (TCA), and impact.

      $\bullet$ Constraints: linear constraints- bound industry/style
      factor exposure, locates, trading limits, position limits, gmv
      utilization, etc. Quadratic constraints- risk, round/odd lot
      optimization, several failed experiments on the quadratic
      constraint side.

      $\bullet$ Added additional factors to risk model as needed/
      requested by investors. Trained additional custom factors for stay at home vs covid recovery loadings, election factors,
      China exposures related factors, Ukraine/ Russia
      factors, etc.

      %% $\bullet$ Overall process: Started with a minimal working
      %% optimizer and added in complexity/ awareness with time (and
      %% substantial backtesting!). For example went from a simple but
      %% conservative quarter spread cost assumption to a tuned, symbol
      %% dependant, cost along with impact estimation.


      $\bullet$ Achieved a consistent 90-95\% idio risk portfolio (to
      USFAST) in backtest, consistent with Live portfolio.
      %% \\$\bullet$ \textbf{CBOE Options Example} - Performed initial analysis of the CBOE trial data set in R. Upon determining that data set was worth
      %% incorporating into our signals I wrote the file ingestion, parsing, and cleaning code in python, then calculated contract level statistics including, greeks,
      %% implied vol, implied price, open interest, volumes, etc. From there I wrote the aggregation functions into symbol level statistics (features) that our alpha would use and fit on.
      %% Regressing the Options signal on the master signal (vs other signals) this sub alpha accounts for roughly 20$\%$ of our overall predictive power. This is a
      %% decently outsized contribution given there are $\sim$10 signals overall.

      \resumeItem{Trading/ Execution}\\

      $\bullet$ Traded over 12 billion USD via 4 execution brokers
      over the last 3 years across $\sim$ 4000 unique publicly traded
      US Equities.

      $\bullet$ As the firm's quant trader I had final sign off
      responsibility to review and submit all trading baskets Bot Lab
      sent to the execution brokers via Schonfeld's OMS (JSON
      interface to fix).

      $\bullet$ Three statically generated baskets of orders per day - open auction, intraday,
      close auction.


      $\bullet$ Research: I developed models to analyze and determine: allocation amongst brokers, allocation amongst trading algos,
      static schedule logic (trade windows, algo instructions, auction participations), etc.
      Additionally, I reviewed execution performance/ TCA's with brokers (and Schonfeld) and incorporated findings into internal work/ trading decisions.



    \resumeItemListEnd
    \vspace{2pt}
    \resumeSubheading
        {Bridgewater Associates}{Glendinning/Westport, CT}
        {Investment Engineer \& Production Integration Engineer}{Dec 2016 -  March 2019}
    \resumeItemListStart
    \resumeItem{Macro Economic Model Updates}
               {Systemized Volume, Open Interest, and Greek Estimates of Brazilian options/futures contracts into Bridgewater's Data and Backtesting platform.}


%    \resumeItem{Investment Engineering Course}
%               {All Investment engineers are given a course which overviewed Asset classes, Macro Economics, Portfolio Theory,
%                 and Bridgewater's framework for evaluating non consenus prices/returns.}
     \resumeItem{Production Integration Engineer - Team Lead}
                {Led a team of six Engineers to assist
                  the Research Department in utilizing Bridgewater's main Backtesting/Signal
                  Generation Platform (Lightspeed), and diagnostic tools (Fusion - advanced UI
                  charting tool). Supported Production Modules and operations team in running
                  live/ production issues. Supported Researchers' various use cases and implementations of logic into the platform.
                  Added functionality to the Investment Engineer/Associate user-facing API as needed.}
    \resumeItemListEnd
    \vspace{2pt}
    \resumeSubheading
        {Nomura}{New York, NY}
        {Technology Analyst}{August 2014 -  November 2016}
        \resumeItemListStart
        \resumeItem{Automation and Support of Structured Products}
                   {Worked on a team to systemize Nomura's Equity Linked Bond business enabling the growth of the book.
                     Helped implement the STP (straight through processing) of notes from
                     issuance to expiration (or redemption). This included pricing/valuation, periodic coupon/ payment analysis, risk analysis / hedging (index and dynamic).
                     Worked alongside a trader and desk quant to help support the growth of the  portfolio to 24 large notional Notes with tenors varying from 1-10 years.}
        \resumeItem{Security Master}{Supported Nomura's Reference database. Rationalized and helped maintain consistency between numerous security identifiers. }
        \resumeItemListEnd

        \resumeSubHeadingListEnd

\end{document}
